General writeup

### 2017-11-25 Latex/general_writeup.tex
Documented that the longer the LR restriction, the more is attributed to IT and less to news

@@

%%%%%%%%	
	\subsection{Capital prices LR horizon 8}
	\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}

>>>>

	\

@@

%%%%%%%%
% LR hor of 16 
\newpage
\subsection{Relative prices LR horizon 16}
	\noindent Time it took, for 500 bootstrap, Mac: 61 min

	\

         \noindent  '0.10054'    '0.60847'    '0.70901'

         \

         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}

         \

\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_19}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_23}}
\end{figure}

%%%%%%%%
% LR hor of 80 - 
\newpage
\subsection{Relative prices LR horizon 80}
	\noindent Time it took, for 500 bootstrap, Mac: 81 min

	\

         \noindent  '0.044546'    '0.69612'    '0.74067'

         \

         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}

         \

\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_10}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_14}}
\end{figure}

%%%%%%%%
%two lags instead of one (back to LR hor = 8)

%%%%%%%%
% adding stock prices

%%%%%%%%
% removing consumption

%%%%%%%%
% and/or adding investment

%%%%%%%%
% Capital prices
\newpage
	\subsection{Capital prices LR horizon 8}
	\noindent Time it took, for 500 bootstrap, Mac: 12 min

	\noindent  Time it took, for 500 bootstrap, server (w/o parpool): 30 min

         \noindent  '0.40843'    '0.23982'    '0.64824'

	\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}

	\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_15}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_19}}
\end{figure}
